The Ranked Nearest Neighbour Interchange space

### 2019-06-10 paper.tex
conj for alg computing trees with max distance from given tree

>>>>

\begin{conjecture}
    Algorithm~\ref{alg:max_dist_tree} computes a tree with maximum distance $\Delta(\rnniu)$ from a given tree $T$.
\end{conjecture}

According to Algorithm~\ref{alg:max_dist_tree}, the number of trees with maximum distance to a given tree $T$ depends on the number of cherries of $T$.
For caterpillar trees it is $(n-1)!$.

\begin{algorithm}[H]
\caption{MAX\_DISTANCE\_TREE($T$)}
\label{alg:max_dist_tree}
\begin{algorithmic}[1]
	\STATE $R$ only contains cherry taxa of $T$ and has internal node with rank $n-1$
    \STATE In list $L$ all taxa $\{1,\ldots,n\}$ are sorted such that the ranks of their parents in $T$ do not decrease
	\FOR {taxon $a$ in $L$}
		\STATE Add an internal node as parent of $a$ on any edge in $R$ such that the new internal node has rank one less than the previously lowest internal node
	\ENDFOR
	\RETURN $R$
\end{algorithmic}
\end{algorithm}
